Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*

### 2022-11-21 data_analysis.Rmd
Finished analyses around the response variable, search distance

@@

```{r packages, echo = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
```

@@

```{r import}
webs <- read.table(file = "data/webs.txt", header = TRUE) 
# includes data for every measured web (multiple per site)
```

@@

```{r webs_wrangling}
# Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph

webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location),
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, 
                                "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
         patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway")

sites <- webs %>% 
  filter(Web == "W001") 
# Restricted to site data only (only one data point per site)
```

```{r sites_wrangling}
# At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future. Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data; a second type of centering and scaling involves subtracting the median and dividing by the interquartile range; need to remember to back transform when making figures; we didn't scale and center because log-transformations on zero-inflated variables were enough to remove convergence errors

sites <- sites %>% 
  mutate(patch_area_km = patch_area_mm * 1e-6)
```

```{r location_subsets}
webs_center <- webs %>% 
  filter(Location == "Urban Center")

@@

Many data are zero-inflated or right skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.

@@

# better log-transformed
ggarrange(ggplot(sites, aes(x = patch_area_km)) +
            geom_density(), 
          ggplot(sites, aes(x = log(patch_area_km))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$patch_area_km) # not normal
shapiro.test(log(sites$patch_area_km)) # almost normal

@@

webs <- webs %>% 
  mutate(log_TotalSub = log(TotalSub),
         log_tdr = log(Traffic_Dist_Road),
         log_tdh = log(Traffic_Dist_Highway),
         log_patch = log(patch_area_km))
```

@@

@@

```{r correlations_overall}
corr <- sites %>% 
  select(tree100m, imperv100m, TotalSub, 
         Traffic_Dist_Road, Traffic_Dist_Highway, 
         spec_rad, light_rad, patch_area_km, road_length_m)
# We exclude trail length from global correlations because trail length can only collected in Wilderness Park, and not for UNL City Campus

@@

# Let's try with the log-transformed
corr_forest_transformed <- sites %>% 
  filter(Location == "Wilderness Park") %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

@@

## Graphs and Stats Comparing Predictors by Location
```{r stats_graphs_tree}
tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites)
summary(tree100m)

@@

ggplot(sites, aes(x = Location, y = tree100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 4, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.25, linewidth = 2) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Tree Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
```

>>>>

Using include = FALSE means that this chunk will run, but the code and the results will not appear in the knitted document. We have set message and warning to FALSE for every chunk so the knitted document is not bombarded with messages and warnings.

@@

There is a brief explanation of each package's purpose left as a comment following the library call.

```{r packages, include = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
```

@@

The document "webs" is a text file in the data folder of the repository/directory.

```{r import, include = FALSE}
webs <- read.table(file = "data/webs.txt", header = TRUE) 
# includes data for every measured web (multiple per site)
```

@@

Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph. We also create another data set "sites" that restricts "webs" to just a single data point for each site. We use "sites" to compare search distance, the number of webs, and the number of spiders. We will use "webs" for web height and nearest neighbor analyses.

```{r webs_wrangling, include = FALSE}
webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location),
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, 
                                "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
         patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway")

sites <- webs %>% 
  filter(Web == "W001") 
```

At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future. Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data; a second type of centering and scaling involves subtracting the median and dividing by the interquartile range; need to remember to back transform when making figures; we didn't scale and center because log-transformations on zero-inflated variables were enough to remove convergence errors

```{r sites_wrangling, include = FALSE}
sites <- sites %>% 
  mutate(patch_area_km = patch_area_mm * 1e-6)
```

@@

Many data are zero-inflated or right skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros. Echo = FALSE shows the results, but does not show the code used.

@@

# better log-transformed
ggarrange(ggplot(sites, aes(x = patch_area_mm)) +
            geom_density(), 
          ggplot(sites, aes(x = log(patch_area_mm))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$patch_area_mm) # not normal
shapiro.test(log(sites$patch_area_mm)) # almost normal

@@

webs <- webs %>% 
  mutate(log_TotalSub = log(TotalSub),
         log_tdr = log(Traffic_Dist_Road),
         log_tdh = log(Traffic_Dist_Highway),
         log_patch = log(patch_area_mm))

sites <- webs %>% 
  filter(Web == "W001") 
```

@@

Our analyses include looking at variation within each location. As such, this chunk subsets the "sites" and "webs" data by Location.

```{r location_subsets, include  = FALSE}
webs_center <- webs %>% 
  filter(Location == "Urban Center")

@@

Since many of these variables are likely highly correlated, we want to reduce the variables that we include in our model by removing variables that are highly correlated.

```{r correlations_overall}
corr <- sites %>% 
  select(tree100m, imperv100m, TotalSub, 
         Traffic_Dist_Road, Traffic_Dist_Highway, 
         spec_rad, light_rad, patch_area_mm, road_length_m)
# We exclude trail length from global correlations because trail length can only collected in Wilderness Park, and not for UNL City Campus

@@

# Let's try with the log-transformed
corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

@@

## Graphs, Stats, and Assumptions Comparing Predictors by Location

Here, we just want to see if each predictor differs between the two Locations: urban forest and urban center. We build models, check assumptions of the model, and make graphs to represent differences.

```{r stats_graphs_tree, echo = FALSE}
tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites)
summary(tree100m)

@@

ggplot(sites, aes(x = Location, y = tree100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Tree Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
```

```{r tree_assumptions, echo = FALSE}
test_tree <- augment(tree100m, data = sites)
resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_tree$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_tree <- ggplot(test_tree, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_tree, qq_tree, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Tree cover is *significantly higher in the urban forest* than the urban center (z = -14.50, df = 1, 20, p < 0.001). The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.

```{r stats_graphs_imperv, echo = FALSE}
imperv100m <- glm(imperv100m ~ Location, family = "poisson", data = sites)
summary(imperv100m)

# The following line tells you the mean and standard error of the raw data for impervious cover in a 100 m radius of the sites between the two locations
sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(imperv100m),
            se = plotrix::std.error(imperv100m))

predictions <- summary(emmeans(imperv100m, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = imperv100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Impervious Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
```

```{r imperv_assumptions, echo = FALSE}
test_imperv <- augment(imperv100m, data = sites)
resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_imperv$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_imperv <- ggplot(test_imperv, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_imperv, qq_imperv, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Impervious cover is *significantly higher in the urban center* than the urban forest (z = 14.51, df = 1, 20, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.

```{r stats_graphs_tdr, echo = FALSE}
tdr <- glm(log_tdr ~ Location, family = "poisson", data = sites)
summary(tdr)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_tdr),
            se = plotrix::std.error(log_tdr))

predictions <- summary(emmeans(tdr, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="", color="black", size = 10)
```

```{r tdr_assumptions, echo = FALSE}
test_tdr <- augment(tdr, data = sites)
resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_tdr$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_tdr <- ggplot(test_tdr, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_tdr, qq_tdr, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

There is *no difference* in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161). The means and SE's are 52.98 ± 1.88 vehicles/day/m for the urban forest and 194.42 ± 1.93 vehicles/day/m for the urban center.

```{r stats_graphs_tdh, echo = FALSE}
tdh <- glm(log_tdh ~ Location, family = "poisson", data = sites)
summary(tdh)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_tdh),
            se = plotrix::std.error(log_tdh))

predictions <- summary(emmeans(tdh, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="", color="black", size = 10)
```

```{r tdh_assumptions, echo = FALSE}
test_tdh <- augment(tdh, data = sites)
resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_tdh$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_tdh <- ggplot(test_tdh, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_tdh, qq_tdh, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

There is *no difference* in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596). The means and SE's are 33.78 ± 1.80 vehicles/day/m for the urban forest and 52.46 ± 1.77 vehicles/day/m for the urban center.

```{r stats_graphs_plant, echo = FALSE}
plant <- glm(log_TotalSub ~ Location, family = "poisson", data = sites)
summary(plant)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_TotalSub),
            se = plotrix::std.error(log_TotalSub))

predictions <- summary(emmeans(plant, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_TotalSub))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
  theme_classic() +
  ylab("Plant Species Richness \n[species/site]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=25, label="*", color="black", size = 10)
```

```{r plant_assumptions, echo = FALSE}
test_plant <- augment(plant, data = sites)
resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_plant$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_plant <- ggplot(test_plant, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_plant, qq_plant, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Plant species richness is *significantly higher in the urban forest* than the urban center (z = -2.430, df = 1, 20, p = 0.015). The means and SE's are 12.18 ± 1.65 species for the urban forest and 2.97 ± 1.35 species for the urban center.

```{r stats_graphs_spec, echo = FALSE}
spec <- glm(spec_rad ~ Location, family = "poisson", data = sites)
summary(spec)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(spec_rad),
            se = plotrix::std.error(spec_rad))

predictions <- summary(emmeans(spec, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = spec_rad)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(130, 165), breaks = c(130, 135, 140, 145, 150, 155, 160, 165)) +
  theme_classic() +
  ylab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=165, label="**", color="black", size = 10)
```

```{r spec_assumptions, echo = FALSE}
test_spec <- augment(plant, data = sites)
resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_spec$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_spec <- ggplot(test_spec, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_spec, qq_spec, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Spectral radiance is *significantly higher in the urban center* than the urban forest (z = 3.079, df = 1, 20, p = 0.002). The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.

```{r stats_graphs_light, echo = FALSE}
light <- glm(light_rad ~ Location, family = "poisson", data = sites)
summary(light)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(light_rad),
            se = plotrix::std.error(light_rad))

predictions <- summary(emmeans(light, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = light_rad)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 175), breaks = c(0, 25, 50, 75, 100, 125, 150, 175)) +
  theme_classic() +
  ylab("Radiance [mcd/m²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=175, label="***", color="black", size = 10)
```

```{r light_assumptions, echo = FALSE}
test_light <- augment(plant, data = sites)
resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_light$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_light <- ggplot(test_light, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_light, qq_light, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Light radiance is *significantly higher in the urban center* than the urban forest (z = 22.46, df = 1, 20, p < 0.001). The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.

```{r stats_graphs_patch, echo = FALSE}
patch <- glm(log_patch ~ Location, family = "poisson", data = sites)
summary(patch)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(log_patch),
            se = plotrix::std.error(log_patch))

predictions <- summary(emmeans(patch, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = exp(log_patch))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = exp(rate - SE), 
                  ymax = exp(rate + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
  theme_classic() +
  ylab("Patch Area [mm²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)
```

```{r patch_assumptions, echo = FALSE}
test_patch <- augment(patch, data = sites)
resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_patch$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_patch <- ggplot(test_patch, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_patch, qq_patch, 
          labels = c("A", "B"),
          ncol = 2, nrow = 1)
```

Patch area is *significantly higher in the urban forest* than the urban center (z = -3.599, df = 1, 20, p < 0.001). The means and SE's are 37,049.12 ± 2.80 mm^2 for the urban forest and 437.03 ± 2.03 mm^2 for the urban center.

```{r stats_graphs_road, echo = FALSE}
road <- glm(road_length_m ~ Location, family = "poisson", data = sites)
summary(road)

sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(road_length_m),
            se = plotrix::std.error(road_length_m))

predictions <- summary(emmeans(road, ~Location),type = "response")
